\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-21 paper2015asml.tex
more introduction

>>>>

Robots working in industrial environments have traditionally been limited to simple, efficient point to point motions. Robotic workcells 
typically require a safety cage to prevent people from being getting close. Robotic motion generation, therefore, does not take 
into account any notion of the acceptability of motions for human observers. The need for more flexibility in manufacturing and logistics, 
though, has resulted in a greater need for robots that can work beside humans. As robots and people start becoming co-workers, taking 
human perception of robotic paths into account will become more important. Humans are able to predict and adjust their motions to 
account for the expectations and motions of their co-workers easily. For human co-workers to be comfortable, robots will similarly 
have to tailor their motions for the presence and actions of the people around them.

In this work, we take a first step towards the ultimate goal of generating robotic motions that are consistent, legible and predictable. Our 
tool of choice is a survey of robot motions where human observers rate the acceptability of the motion. We generated a range of trajectories 
across multiple environments with different planners. Movies of these trajectories from multiple viewpoints were then presented to human 
observers using an online survey tool. The users were asked to rate different attributes of the trajectories. We
